\chapter{Analysis Of Existing}

Comme dit auparavant, les flottes de drones sont régis entres elles par des modèles de mobilités. Notre étude de l'existant s'est donc décomposée en plusieurs parties.\\\\

As said before, fleets drones are governed by these models mobility. Our study of the current is therefore divided into several parts. \ \ \ \

\section{Summary of the problem}

La problématique de notre article est de scanner une zone le plus efficacement possible et le plus rapidement possible, au maximum une fois par heure. Cette zone sera scannée par une flotte de drone qui devront coopérer entre eux et communiquer.\\\\

The issue of this paper is to scan an area as efficiently as possible and as quickly as possible, at most once per hour. This area will be scanned by a fleet of drones that will cooperate and communicate.\\\\


\section{Existing models}

De nombreux modèles de mobilité existent avec chacun des caractéristiques différentes. Tous ces modèles permettent de définir des mouvements à des flottes de drones. La plupart des modèles sont basés sur des situations de la vie réelle comme la cartographie routière, ou encore sur le comportement de nombreux animaux (fourmis, oiseaux, thermites etc). Nous allons vous en exposer certains que nous considérons les plus importants et les plus intéressants pour notre cas.\\\\

Many mobility models exist each with different characteristics. All these models are used to define movements fleets drones. Most models are based on real-life situations such as road maps, or on the behavior of many animals (ants, birds, termites, wolves etc). We will expose some of which we consider the most important and most interesting for our case.\\\\ 

\subsection{Random Walk}

First described by Einstein in 1926 [29], it was developed to mimic the extremely unpredictable movement of many entities in nature [9]. An MN moves from its position to a new one by randomly choosing a direction and speed choosen by pre-defined ranges, [speedmin, speedmax] and [0, 2PI]. At the end of a constant time interval t or a constant distance traveled d, a new speed and direction are calculated. If a MN during his travel reaches a simulation boundary, it « bounces » off the simulation border with an angle determined by the incoming direction and continues to this new path.
It's a memoryless mobility pattern because it retains no knowledge of its old locations and speed values [19]. Therefore, the current position and speed of a MN is independent of its past location and speed. This can generate unrealistic movement because of sudden stops and sharp turns. If the specified time or distance of a MN motion is short, the area of the simulation will be small.

\textbf{METTRE DES SCHEMA ET DECRIRE PLUS}

\subsection{Random Waypoint}

Includes pause times between changes in direction and/or speed.Once this time expires, the MN chooses a random destination and a speed, that is uniformly distributed between [minspeed, maxspeed]. The movement pattern of a MN who uses the RWaypointMM is similar to the RwalkMM if pause time is zero and [minspeed, maxspeed] = [speedmin, speedmax].
During a performance investigation, MNs are initially distributed randomly around the simulation area. Figure 4 shows the average MN neighbor percentage of the MNs. For example, if there are 50 MNs in the network and a node has 10 neighborns, then the node's current neighbor percentage is 20\%. Moreover, during the first 600 seconds, due to initially distributed randomly of the MNs around the simulation area, there is an high variability in the average MN neighbor percentage.
In the paper, there is presented three possible solutions to avoid this initialization problem. The first is to save the location of the MNs after the initial high variability and use this position as the initial starting point of the MNs in all future simulations. Second, initially distribute the MNs in a specific area to be a distribution more common the model, like fore example, initially placing the MNs in a triangle distribution. Lastly, discard the initial 1000 seconds of simulation time in each simulation trials, to ensure thatthe initialization problem is removed even if the MNs move slowly. But if the MNs move fastly, we can discard fewer seconds of simulation time. This third solution ensures that each simulation has a random initial configuration.
Figure 5 : thre is a complex relationship between node speed and pause time. A scenario with fast MNs and long pause times actually produces a more stable networks than a scenario with slower MNs and shorter pause times. Hence, long pause times(over 20 seconds) produce a stable network even at high speeds.

\textbf{METTRE DES SCHEMA ET a revoir}

\subsection{City section}

Similar to Random Waypoint MM but here, the simulation area is a city where the ad hoc network exists and each MN begins the simu at a defined point( opposite to RwaypointMM) on some street of the city. There exists also safe driving characteristics such as a speed limit or minimum distance allowed between the current position and the new location.

\textbf{METTRE DES SCHEMA ET a compléter}

\subsection{Natural Agent}

\subsubsection{Ants}

Le modèle de mobilité des fourmis se base sur le fait que les fourmis construisent des réseaux de sentiers qui relient leurs   nids avec des sources de nourritures disponible.
Chaque fourmi qui se nourrit à le même programme :

\begin{itemize}
\item Elle doit éviter les obstacles.
\item Aller ou elle veut (déplacement aléatoire) tant qu'il n'y a pas de phéromones.
\item Si elle arrive à trouver de la nourriture, elle laisse des phéromones pendant un temps t pour pouvoir indiquer aux autres fourmis l'emplacement de la nourriture.
\item Si la fourmi trouve de la nourriture, elle l'a ramène à son nid.
\end{itemize}

Les fourmis peuvent mourir. Soit elles ne trouvent pas de la nourriture assez rapidement et meurt de faim, soit elles se font tuer par d'autres prédateurs.
Tous les chemins de phéromones conduisent à de la nourriture. Mais les phéromones s'évaporent dans le temps. Le taux de phéromone peut être renforcé si plusieurs fourmis passent par le même chemin.

\textbf{METTRE DES SCHEMA ET a compléter}

\subsubsection{Termites}

\subsubsection{Wasps}

le modèle basé sur les guêpes est composé de plusieurs caractéristiques :
\begin{itemize}
\item un chef qui répartit les différentes guêpes dans différents groupes
\item 
\end{itemize}

\subsection{Birds and Fish}

\subsection{Wolves}

 